 

### 2023-05-15 appendix_2.1.Rmd
Additional typesettting changes

While primary, district, and regional referral facilities in Madagascar all reported monthly visits related to mental disorders in \acr{GESIS}, case definitions varied across facilities of different levels. Disaggregated data by specific condition (e.g., depression, schizophrenia, etc.) were only reported among regional referral hospitals and university hospitals; for all other facilities, visit by type of mental heath complaint were reported in aggregate (e.g., "Neuro-psychic diseases" for district hospitals).

Disaggregated data was available by age; among adults, however, disaggregated data for adults ages 25 to 59 and adults 60 years and older was only reported by primary health facilities after 2015. For all other years and all other facilities, these age categories were not separately reported. Similarly, data by sex was only reported for primary health facilities after 2015. Referrals were reported by primary health facilities and district hospitals.

@@

Visual inspect of our data showed potential outliers, which may have arisen due to data entry mistakes, synchronization errors, and other sources. To address outliers, monthly observations of the outcome were arranged separately for each facility into a unique time series. The nonparametric Friedman’s super smoother regression estimator [@friedmanVariableSpanScatterplot1984] was applied to each time series to identify outlier observations and replace them through linear interpolation [@hyndmanAutomaticTimeSeries2008]. By considering outliers on a facility-by-facility basis, the data cleaning approach preserved extreme values that may have reflected true variances in visit counts (for example, visits reported by a large, regional reference hospital) while addressing potential errors in data entry. Interpolated values were coerced to the nearest integer.

>>>>

While primary, district, and regional referral facilities in Madagascar all reported monthly visits related to mental disorders in \acr{GESIS}, case definitions varied across facilities of different levels. Disaggregated data by specific condition (e.g., depression, schizophrenia, etc.) were only reported among regional referral hospitals and university hospitals; for all other facilities, visits by type of mental heath complaint were reported in aggregate (e.g., "Neuro-psychic diseases" for district hospitals).

Disaggregated data were available by age; among adults, however, disaggregated data for adults ages 25 to 59 and adults 60 years and older were only reported by primary health facilities after 2015. For all other years and all other facilities, these age categories were not separately reported. Similarly, data by sex were only reported for primary health facilities after 2015. Referrals were reported by primary health facilities and district hospitals.

@@

Visual inspection of our data showed potential outliers, which may have arisen due to data entry mistakes, synchronization errors, and other sources. To address outliers, monthly observations of the outcome were arranged separately for each facility into a unique time series. The nonparametric Friedman’s super smoother regression estimator [@friedmanVariableSpanScatterplot1984] was applied to each time series to identify outlier observations and replace them through linear interpolation [@hyndmanAutomaticTimeSeries2008]. By considering outliers on a facility-by-facility basis, the data cleaning approach preserved extreme values that may have reflected true variances in visit counts (for example, visits reported by a large, regional reference hospital) while addressing potential errors in data entry. Interpolated values were rounded to the nearest integer.
